---
title: "Accessibility Fails"
date: "23 August 2016"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = FALSE
  )

# Reproducibility stuff

library(checkpoint)
setSnapshot('2016-08-22')

# Load packages

library(dplyr)
library(readr)
library(digest)
library(magrittr)
library(ggplot2)
library(knitr)

# Load tools script

source('tools.R')
```

# How to read the tables?

* Tables show the maximum number of accessibility fails found (**score**) for a given number of automated tools (**n_tools**).
* Several combinations of the same number of tools may yield the same score.  
* Since the automated tools have three outputs of interest: error found, warning reported, and flagging for manual inspection, three tables are presented with combinations of these:
    * error found  
    * error found + warning reported  
    * error found + warning reported + allows manual inspection.  

# How to read the plots

The plots demonstrate how increasing the number of tools used will not necessarily increase the number of fails found.
Typically, using seven tools will not increase the number of fails found.

# Error found

```{r}

fails_data <- 'accessibility_fail_data.csv' %>%
  read_csv %>%  
  dplyr::select(
    -WCAG_Level
  )


tool_names = names(fails_data)[-1]
names(tool_names) <- 1:length(tool_names)

outcomes <- c('error_found','warning_reported','allows_manual_inspection')

```

```{r}

output <- 1:10 %>%
  purrr::map_df(
    ~ foobar(x = .x, paste0('^',outcomes[1],'$')), 
    .id = "n_tools"
  ) %>%
  set_colnames(
    c('n_tools', 'score', 'tools')
  ) %>%
  tidyr::separate(
    tools,
    into = as.character(1:10)
  ) %>%
  as_data_frame %>%
  mutate_each(
    funs = funs(as.integer),
    3:12
  ) %>%
  mutate_each(
    funs = funs(argh),
    3:12
  )

output1 <- output %>%
  group_by(n_tools = as.integer(n_tools)) %>%
  dplyr::mutate(
    max = max(score)
  ) %>%
  dplyr::filter(
    score == max
    ) %>%
  select(-max)

output1 %>%
  kable

output1 %>%
  ggplot + 
  aes(
    x = n_tools,
    y = score,
    group = 1
  ) +
  geom_line() +
  xlab('Number of tools used') +
  ylab('Total number of fails identified') +
  scale_x_continuous(breaks = 1:10)  +
  ggtitle(paste(outcomes[1], collapse = ' + '))
```

# Error found + warning reported

```{r}

output <- 1:10 %>%
  purrr::map_df(
    ~ foobar(x = .x, paste0('^',outcomes[1:2],'$')), 
    .id = "n_tools"
  ) %>%
  set_colnames(
    c('n_tools', 'score', 'tools')
  ) %>%
  tidyr::separate(
    tools,
    into = as.character(1:10)
  ) %>%
  as_data_frame %>%
  mutate_each(
    funs = funs(as.integer),
    3:12
  ) %>%
  mutate_each(
    funs = funs(argh),
    3:12
  )

output1 <- output %>%
  group_by(n_tools = as.integer(n_tools)) %>%
  dplyr::mutate(
    max = max(score)
  ) %>%
  dplyr::filter(
    score == max
    )  %>%
  select(-max)

output1 %>%
  kable

output1 %>%
  ggplot + 
  aes(
    x = n_tools,
    y = score,
    group = 1
  ) +
  geom_line() +
  xlab('Number of tools used') +
  ylab('Total number of fails identified') +
  scale_x_continuous(breaks = 1:10)  +
  ggtitle(paste(outcomes[1:2], collapse = ' + '))
```

# Error found + warning reported + allows manual inspection

```{r}

output <- 1:10 %>%
  purrr::map_df(
    ~ foobar(x = .x, paste0('^',outcomes[1:3],'$')), 
    .id = "n_tools"
  ) %>%
  set_colnames(
    c('n_tools', 'score', 'tools')
  ) %>%
  tidyr::separate(
    tools,
    into = as.character(1:10)
  ) %>%
  as_data_frame %>%
  mutate_each(
    funs = funs(as.integer),
    3:12
  ) %>%
  mutate_each(
    funs = funs(argh),
    3:12
  )

output1 <- output %>%
  group_by(n_tools = as.integer(n_tools)) %>%
  dplyr::mutate(
    max = max(score)
  ) %>%
  dplyr::filter(
    score == max
    )  %>%
  select(-max)

output1 %>%
  kable

output1 %>%
  ggplot + 
  aes(
    x = n_tools,
    y = score,
    group = 1
  ) +
  geom_line() +
  xlab('Number of tools used') +
  ylab('Total number of fails identified') +
  scale_x_continuous(breaks = 1:10) +
  ggtitle(paste(outcomes[1:3], collapse = ' + '))
```
